---
title: "Run VCAP through huskeR"
output: html_notebook
date: 02-13-2019
---

## VCAP using BED file

The BED file genome coordinates should be 0-based with the chromStart inclusive and the chromEnd exclusive (see https://genome.ucsc.edu/FAQ/FAQformat.html#format1). Note that Ensembl genome database, gff3, gtf, and Tassel5 coordinates are 1-based (and gff3 and gtf ranges are start and end-inclusive). A simple way to go from Ensemble/gff3/gtf/Tassel coordinates to BED file coordinates without subtracting 1 is to think of the BED file coordinates as 1-based but with start exclusive and end inclusive. Hence, a BED file range with chromStart = 5000 and chromEnd = 5100 includes chromosomal positions ≥ 5001 and ≤ 5100 in terms of a Tassel genotype file. The coordinate system (i.e., AGPv3) should be consistent between the BED and genotype files.


Fron Gen: in the below folder:
`largedata/DMR_Features_Overlap`


From Thomas:
For GWAS the idea was to have K1) promotor_5kb;  K2) promotor_1kb + 5' UTR;  K3) Exon + Intron;    K4) 3' UTR + post_gene_1kb;   K5) far from genes (non_genic)
We have to check if combining K1) and K2) gives us better or weeker statistics over bgSNPs.


### CG

- 5kb
- exonic
- intronic
- 

### Maize and Teosinte CG

```{r, eval=FALSE}

files <- list.files("largedata/DMR_Features_Overlap/AGPV3", full.names = TRUE, pattern="bed")

df <- data.frame(f=files, pop="maize")

idx <- grep("CG_teosinte_maize", df$f)
df1 <- df[idx, ]

# copy the files to the new folder
file.copy(as.character(df1$f), "largedata/VCAP/test")

```

### Run VCAP via huskeR

```{R, eval=FALSE}

library("huskeR")
df <- data.frame(bedfile1="largedata/VCAP/test/CG_teosinte_maize_3UTR_overlap.bed",
                 bedfile2="largedata/VCAP/test/CG_teosinte_maize_5UTR_overlap.bed",
                 bedfile3="largedata/VCAP/test/CG_teosinte_maize_exon_overlap.bed",
                 bedfile4="largedata/VCAP/test/CG_teosinte_maize_intron_overlap.bed",
                 bedfile5="largedata/VCAP/test/CG_teosinte_maize_gen_downstr_2k_overlap.bed",
                 bedfile6="largedata/VCAP/test/CG_teosinte_maize_gen_upstr_2k_overlap.bed",
                 bedfile7="largedata/VCAP/test/CG_teosinte_maize_intergenic_overlap.bed",
                 bedfile8="largedata/VCAP/test/CG_teosinte_maize_TE_overlap.bed",
                 gz.lix="/common/jyanglab/shared/dbcenter/RareAlleles/genomeAnnos/VCAP/genotypes/NAM/namrils_projected_hmp31_MAF02mnCnt2500.hmp.txt.gz.lix",
                 genome_kinship="/common/jyanglab/shared/dbcenter/RareAlleles/genomeAnnos/VCAP/kinship/NAM_HM31_MAF02mnCnt2500_WholeGenomeCentered_IBS_SqrMatrix.txt",
                 res_kinship="largedata/VCAP/test"
                 )

run_VCAP(df, email = "yangjl0930@gmail.com", jobid = "run_vcap", runinfo = c(TRUE,
       "jclarke", "10", "50G", "3:00:00"))

```

### Run LDAK

Using R package `huskeR`:

```{r, eval=FALSE}
library("huskeR")

### get kinship list
kfile <- list.files(path="largedata/VCAP/test", pattern="N.bin", full.names=TRUE)
d <- data.frame(kin=gsub(".grm.N.bin", "", kfile))
write.table(d, "largedata/VCAP/kinship/teo-maize-CG_klist.txt", sep="\t", 
            row.names=FALSE, col.names=FALSE, quote=FALSE)

###
pheno <- list.files(path="/common/jyanglab/shared/dbcenter/RareAlleles/genomeAnnos/VCAP/phenotypes/NAM/familyCorrected", pattern="NAM", full.names=TRUE)

df <- data.frame(output="largedata/VCAP/h2_teo-maize/", klist="largedata/VCAP/kinship/teo-maize-CG_klist.txt", pheno=pheno)
df$output <- paste0(df$output, gsub(".*\\/|.txt", "", df$pheno))

run_ldak(df, email="yangjl0930@gmail.com", runinfo=c(TRUE, "jclarke", "2", "10G", "8:00:00"))

```

## get Results

```{r, eval=FALSE}
files <- list.files(path="largedata/VCAP/h2_teo-maize", pattern="reml", full.names=TRUE)

out <- data.frame()
for(i in 1:length(files)){
  h2 <- read.table(files[i], skip=13, header=TRUE)
  th2 <- as.data.frame(t(h2[-7, 1:2]))
  names(th2) <- as.character(h2$Component[-7])
  th2$trait <- files[i]
  out <- rbind(out, th2[-1, ])
}

out$trait <- gsub(".*NAM_|_famC.*", "", out$trait)
tkey <- read.delim("/common/jyanglab/shared/dbcenter/RareAlleles/genomeAnnos/VCAP/phenotypes/NAM/familyCorrected/trait_name_key.txt", header=T)

out <- merge(out, tkey, by.x="trait", by.y="raw_name")
out$Her_ALL <- as.numeric(as.character(out$Her_ALL))
out1 <- subset(out, Her_ALL > 0.4)
write.table(out, "cache/h2_teo-maize_CG.csv", sep=",", row.names=FALSE, quote=FALSE)
```


