---
title: "Run VCAP through huskeR"
output: html_notebook
date: 02-22-2019
author: "Jinliang Yang"
---


### Maize and Teosinte CG

02192022 version:
five mutually exclusive features:
1. gene body
2. downstream 5k
3. upstream 5k
4. intergenic
5. TE

### Run LDAK

Using R package `huskeR`:

```{r, eval=FALSE}
library("huskeR", lib.loc = "~/R/x86_64-pc-linux-gnu-library/3.5")

run_batch_ldak_sample <- function(sid=1:10, traits, runinfo=c(TRUE, "jyanglab", "2", "10G", "8:00:00"),
  dmr_patterns = c("CG_teosinte_maize", "CHG_teosinte_maize", "CHH_teosinte_maize",
                  "CG_landrace_maize", "CHG_landrace_maize", "CHH_landrace_maize",
                  "CG_teosinte_landrace", "CHG_teosinte_landrace", "CHH_teosinte_landrace")
  ){
  
  df <- data.frame()
  ###
  pheno <- list.files(path="/common/jyanglab/shared/dbcenter/RareAlleles/genomeAnnos/VCAP/phenotypes/NAM/familyCorrected", pattern="NAM", full.names=TRUE)
  ph <- data.frame(pheno, trait=1)
  ph$trait <- as.character(gsub(".*/NAM_|_famCorrected.txt", "", ph$pheno))
  ph <- subset(ph, trait %in% as.character(traits))
    
  ### get kinship list
  for(i in 1:length(dmr_patterns)){
    
    df1 <- data.frame()
    for(j in 1:length(sid)){
      ### write out kinship list file
      kinship_dir <- paste0("largedata/VCAP/", dmr_patterns[i], "/sample/S", j, "/bedfile")
      
      kfile <- list.files(path=kinship_dir, pattern="N.bin", full.names=TRUE)
      d <- data.frame(kin=gsub(".grm.N.bin", "", kfile))
      write.table(d, paste0(kinship_dir, "/kinlist.txt"), sep="\t", 
            row.names=FALSE, col.names=FALSE, quote=FALSE)
      
      output_h2 <- gsub("bedfile", "h2/", kinship_dir)
      dir.create(output_h2, showWarnings = FALSE)
      tem <- data.frame(output=output_h2, klist=paste0(kinship_dir, "/kinlist.txt"), pheno=ph$pheno)
      tem$output <- paste0(tem$output, gsub(".*\\/|.txt", "", tem$pheno))
      df1 <- rbind(df1, tem)
    }
    df <- rbind(df, df1)
  }
  
  run_ldak(df, email="yangjl0930@gmail.com", runinfo=runinfo)
}


```


## This step only for traits of interests

                                                                                             V1
1       largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_body_overlap.bed.kinship
2 largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_downstr_5k_overlap.bed.kinship
3   largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_upstr_5k_overlap.bed.kinship
4     largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_intergenic_overlap.bed.kinship
5             largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_TE_overlap.bed.kinship
6                                            largedata/VCAP/CG_landrace_maize/bedfile/rest_geno

K1: gene body
K2: downstream 5k
K3: upstream 5k
K4: intergenic
K5: TE
```{r}
res <- read.csv("cache/h2_CG_teosinte_maize.csv")
t <- subset(res, h2 > 0.05) # 16

run_batch_ldak_sample(sid=1:100, traits= as.character(t$trait[1:8]), 
                      runinfo=c(TRUE, "jyanglab", "2", "10G", "8:00:00"), 
                      dmr_patterns = "CG_teosinte_maize")

res <- read.csv("cache/h2_CG_teosinte_maize.csv")
t <- subset(res, h2 > 0.05) # 16

run_batch_ldak_sample(sid=1:100, traits= as.character(t$trait[9:16]), 
                      runinfo=c(TRUE, "jyanglab", "2", "10G", "8:00:00"), 
                      dmr_patterns = "CG_teosinte_maize")


```

## 2-23-2019: 
```{r}
res <- read.csv("cache/h2_CG_teosinte_landrace.csv")
t <- subset(res, h2 > 0.05) # 7

run_batch_ldak_sample(sid=1:100, traits= as.character(t$trait), 
                      runinfo=c(TRUE, "jclarke", "2", "10G", "8:00:00"), 
                      dmr_patterns = "CG_teosinte_landrace")


```
