---
title: "Clean VCAP results"
output: NULL
date: 09-28-2019
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```


## get Results
                                                                                             V1
1       largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_body_overlap.bed.kinship
2 largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_downstr_5k_overlap.bed.kinship
3   largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_upstr_5k_overlap.bed.kinship
4     largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_intergenic_overlap.bed.kinship
5             largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_TE_overlap.bed.kinship
6                                            largedata/VCAP/CG_landrace_maize/bedfile/rest_geno


### Bar plot

CG teosinte and maize
```{r}

library("dplyr")
library("tidyr")
library("ggplot2")


clean_VCAP_data <- function(infile="cache/h2_CG_teosinte_maize.csv", outfile="cache/h2_CG_teosinte_maize_cleaned.csv"){
  cg1 <- read.csv(infile)
  cg1 <- subset(cg1, !is.na(pretty_name))
  cg1$trait <- as.character(cg1$trait)
  cg1$pretty_name <- as.character(cg1$pretty_name)
  #cg1[is.na(cg1$pretty_name), ]$pretty_name <- cg1[is.na(cg1$pretty_name), ]$trait
  subcg1 <- cg1[, c("pretty_name", "h2", "Her_K6", "Her_K1", "Her_K2", "Her_K3", "Her_K4", "Her_K5")]
  subcg1 <- subcg1[order(subcg1$h2, decreasing = F),]
  subcg1$Her_K6 <- -abs(subcg1$Her_K6)
  subcg1$od <- 1:nrow(subcg1)
  
  #subcg1 <- subcg1[order(subcg1$h2, decreasing = TRUE),]
  
  subcg1$pretty_name <- factor(subcg1$pretty_name,  levels=subcg1$pretty_name)
  df <- gather(data=subcg1[, c(1:3, ncol(subcg1))], key=k, value="var", 2:3)
  
  df[!(df$k %in% "Her_K6"), ]$k <- "DMR"
  df[df$k %in% "Her_K6", ]$k <- "non-DMR"
  write.table(df, outfile, sep=",", row.names=FALSE, quote=FALSE)

}




clean_VCAP_data(infile="cache/h2_CG_teosinte_maize.csv", outfile="cache/h2_CG_teosinte_maize_cleaned.csv")
clean_VCAP_data(infile="cache/h2_CHG_teosinte_maize.csv", outfile="cache/h2_CHG_teosinte_maize_cleaned.csv")
clean_VCAP_data(infile="cache/h2_CHH_teosinte_maize.csv", outfile="cache/h2_CHH_teosinte_maize_cleaned.csv")

clean_VCAP_data(infile="cache/h2_CG_teosinte_landrace.csv", outfile="cache/h2_CG_teosinte_landrace_cleaned.csv")
clean_VCAP_data(infile="cache/h2_CHG_teosinte_landrace.csv", outfile="cache/h2_CHG_teosinte_landrace_cleaned.csv")
clean_VCAP_data(infile="cache/h2_CHH_teosinte_landrace.csv", outfile="cache/h2_CHH_teosinte_landrace_cleaned.csv")


clean_VCAP_data(infile="cache/h2_CG_landrace_maize.csv", outfile="cache/h2_CG_landrace_maize_cleaned.csv")
clean_VCAP_data(infile="cache/h2_CHG_landrace_maize.csv", outfile="cache/h2_CHG_landrace_maize_cleaned.csv")
clean_VCAP_data(infile="cache/h2_CHH_landrace_maize.csv", outfile="cache/h2_CHH_landrace_maize_cleaned.csv")


```

