---
title: "Obtain results"
output: html_notebook
date: 02-22-2019
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```


## get Results
                                                                                             V1
1       largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_body_overlap.bed.kinship
2 largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_downstr_5k_overlap.bed.kinship
3   largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_upstr_5k_overlap.bed.kinship
4     largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_intergenic_overlap.bed.kinship
5             largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_TE_overlap.bed.kinship
6                                            largedata/VCAP/CG_landrace_maize/bedfile/rest_geno


### Bar plot

CHG teosinte and landrace
```{r}

library("dplyr")
library("tidyr")
library("ggplot2")


mybarplot <- function(df){
  cg1 <- df
  cg1$trait <- as.character(cg1$trait)
  cg1$pretty_name <- as.character(cg1$pretty_name)
  cg1[is.na(cg1$pretty_name), ]$pretty_name <- cg1[is.na(cg1$pretty_name), ]$trait
  subcg1 <- cg1[, c("pretty_name", "h2", "Her_K6", "Her_K1", "Her_K2", "Her_K3", "Her_K4", "Her_K5")]
  subcg1 <- subcg1[order(subcg1$h2, decreasing = F),]
  subcg1$Her_K6 <- -abs(subcg1$Her_K6)
  subcg1$od <- 1:nrow(subcg1)

  subcg1$pretty_name <- factor(subcg1$pretty_name,  levels=subcg1$pretty_name)
  df <- gather(data=subcg1, key=k, value="var", 3:8)
  
  p <- ggplot(df, aes(x=pretty_name, y=var, fill=k), position = position_stack(reverse = TRUE)) +
    geom_bar(stat="identity") +
    coord_flip() +
    theme_bw() +
    xlab("") +
    ylab("") +
    geom_hline(yintercept=0.1, linetype="dotted") +
    scale_x_discrete(position = "top") +
    geom_vline(xintercept=0.1, linetype="dotted") +
    # https://www.color-hex.com/color-palette/73961
    scale_fill_manual(values=c("#cc4141", "#72114b", "#e1cd07", "#5f9057", "#114c63", "#d3d3d3"),
                      name=c(""),
                      labels=c("Gene", "Down 5k", "Up 5k", "Intergenic", "TE", "Rest")) +
    #scale_fill_discrete(name="", labels=c("Exon", "Intron")) +
    theme(legend.position="top", axis.text=element_text(size=12), axis.title=element_text(size=15) )
  #########
  return(p)
}



chg1 <- read.csv("cache/h2_CHG_teosinte_maize.csv")

pdf("graphs/barplot_CHG_teosinte_maize.pdf", width = 8, height=8)
mybarplot(df=chg1)
dev.off()  

chg2 <- read.csv("cache/h2_CHG_teosinte_landrace.csv")
pdf("graphs/barplot_CHG_teosinte_landrace.pdf", width = 8, height=8)
mybarplot(df=chg2)
dev.off()  

chg3 <- read.csv("cache/h2_CHG_landrace_maize.csv")
pdf("graphs/barplot_CHG_landrace_maize.pdf", width = 8, height=8)
mybarplot(df=chg3)
dev.off()  

```

CG teosinte and landrace
```{r}
cg1 <- chg2
cg1$trait <- as.character(cg1$trait)
cg1$pretty_name <- as.character(cg1$pretty_name)
cg1[is.na(cg1$pretty_name), ]$pretty_name <- cg1[is.na(cg1$pretty_name), ]$trait
subcg1 <- cg1[, c("pretty_name", "h2", "Her_K6", "Her_K1", "Her_K2", "Her_K3", "Her_K4", "Her_K5")]
subcg1 <- subcg1[order(subcg1$h2, decreasing = F),]
subcg1$Her_K6 <- -abs(subcg1$Her_K6)
subcg1$od <- 1:nrow(subcg1)

subcg1$pretty_name <- factor(subcg1$pretty_name,  levels=subcg1$pretty_name)
df <- gather(data=subcg1, key=k, value="var", 3:8)
  
p <- ggplot(df, aes(x=pretty_name, y=var, fill=k), position = position_stack(reverse = TRUE)) +
    geom_bar(stat="identity") +
    coord_flip() +
    theme_bw() +
    xlab("") +
    ylab("") +
    geom_hline(yintercept=0.1, linetype="dotted") +
    scale_x_discrete(position = "top") +
    geom_vline(xintercept=0.1, linetype="dotted") +
    # https://www.color-hex.com/color-palette/73961
    scale_fill_manual(values=c("#cc4141", "#72114b", "#e1cd07", "#5f9057", "#114c63", "#d3d3d3"),
                      name=c(""),
                      labels=c("Gene", "Down 5k", "Up 5k", "Intergenic", "TE", "Rest")) +
    #scale_fill_discrete(name="", labels=c("Exon", "Intron")) +
    theme(legend.position="top", axis.text=element_text(size=12), axis.title=element_text(size=15) )
#########
p

```

CG landrace and maize
```{r}
cg1 <- chg3
cg1$trait <- as.character(cg1$trait)
cg1$pretty_name <- as.character(cg1$pretty_name)
cg1[is.na(cg1$pretty_name), ]$pretty_name <- cg1[is.na(cg1$pretty_name), ]$trait
subcg1 <- cg1[, c("pretty_name", "h2", "Her_K6", "Her_K1", "Her_K2", "Her_K3", "Her_K4", "Her_K5")]
subcg1 <- subcg1[order(subcg1$h2, decreasing = F),]
subcg1$Her_K6 <- -abs(subcg1$Her_K6)
subcg1$od <- 1:nrow(subcg1)

subcg1$pretty_name <- factor(subcg1$pretty_name,  levels=subcg1$pretty_name)
df <- gather(data=subcg1, key=k, value="var", 3:8)
  
p <- ggplot(df, aes(x=pretty_name, y=var, fill=k), position = position_stack(reverse = TRUE)) +
    geom_bar(stat="identity") +
    coord_flip() +
    theme_bw() +
    xlab("") +
    ylab("") +
    geom_hline(yintercept=0.1, linetype="dotted") +
    scale_x_discrete(position = "top") +
    geom_vline(xintercept=0.1, linetype="dotted") +
    # https://www.color-hex.com/color-palette/73961
    scale_fill_manual(values=c("#cc4141", "#72114b", "#e1cd07", "#5f9057", "#114c63", "#d3d3d3"),
                      name=c(""),
                      labels=c("Gene", "Down 5k", "Up 5k", "Intergenic", "TE", "Rest")) +
    #scale_fill_discrete(name="", labels=c("Exon", "Intron")) +
    theme(legend.position="top", axis.text=element_text(size=12), axis.title=element_text(size=15) )
#########
p
```






