---
title: "Obtain results"
output: html_notebook
date: 02-22-2019
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```


## get Results
                                                                                             V1
1       largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_body_overlap.bed.kinship
2 largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_downstr_5k_overlap.bed.kinship
3   largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_upstr_5k_overlap.bed.kinship
4     largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_intergenic_overlap.bed.kinship
5             largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_TE_overlap.bed.kinship
6                                            largedata/VCAP/CG_landrace_maize/bedfile/rest_geno

```{r, eval=FALSE}

get_h2 <- function(pwd="largedata/VCAP/CG_teosinte_maize/sample", 
                   outfile="cache/h2_CG_teosinte_maize_sample.csv"){
  
  files <- list.files(path=pwd, recursive = T, pattern="reml", full.names=TRUE)

  #klist <- read.table("largedata/VCAP/CG_landrace_maize/bedfile/kinlist.txt", header=F)
  out <- data.frame()
  for(i in 1:length(files)){
    h2 <- read.table(files[i], skip=13, header=TRUE)
    th2 <- as.data.frame(t(h2[-7, 1:2]))
    names(th2) <- as.character(h2$Component[-7])
    th2$trait <- files[i]
    out <- rbind(out, th2[-1, ])
  }
  
  out$context <- gsub(".*VCAP\\/", "", out$trait)
  out$context <- gsub("\\/.*", "", out$context)
  
  out$rep <- gsub(".*sample\\/", "", out$trait)
  out$rep <- gsub("\\/.*", "", out$rep)
  
  out$trait <- gsub(".*NAM_|_famC.*", "", out$trait)
  tkey <- read.delim("/common/jyanglab/shared/dbcenter/RareAlleles/genomeAnnos/VCAP/phenotypes/NAM/familyCorrected/trait_name_key.txt", header=T)
  
  out <- merge(out, tkey, by.x="trait", by.y="raw_name", all.x=TRUE)
  out$trait <- as.character(out$trait)
  out <- subset(out, !(trait %in% "Residual_boxcox_noIBM"))
  
  for(j in 2:6){
    out[, j] <- as.numeric(as.character(out[,j]))
    #out[out[,j] < 0, j] <- 0
  }
  
  out$h2 <- out$Her_K1 + out$Her_K2 + out$Her_K3 + out$Her_K4 + out$Her_K5
  print(table(out$rep))
  write.table(out, outfile, sep=",", row.names=FALSE, quote=FALSE)
}


```

```{r}
get_h2(pwd="largedata/VCAP/CG_teosinte_maize/sample", outfile="cache/h2_CG_teosinte_maize_sample.csv")

get_h2(pwd="largedata/VCAP/CG_teosinte_landrace/sample", outfile="cache/h2_CG_teosinte_landrace.csv")
#get_h2(pwd="largedata/VCAP/CHH_teosinte_maize/h2", outfile="cache/h2_CHH_teosinte_maize.csv")






get_h2(pwd="largedata/VCAP/CG_teosinte_landrace/h2", outfile="cache/h2_CG_teosinte_landrace.csv")
get_h2(pwd="largedata/VCAP/CHG_teosinte_landrace/h2", outfile="cache/h2_CHG_teosinte_landrace.csv")
#get_h2(pwd="largedata/VCAP/CHH_teosinte_landrace/h2", outfile="cache/h2_CHH_teosinte_landrace.csv")

get_h2(pwd="largedata/VCAP/CG_landrace_maize/h2", outfile="cache/h2_CG_landrace_maize.csv")
get_h2(pwd="largedata/VCAP/CHG_landrace_maize/h2", outfile="cache/h2_CHG_landrace_maize.csv")
#get_h2(pwd="largedata/VCAP/CHH_landrace_maize/h2", outfile="cache/h2_CHH_landrace_maize.csv")


```


