---
title: "Obtain results"
output: html_notebook
date: 02-22-2019
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```


## get Results
                                                                                             V1
1       largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_body_overlap.bed.kinship
2 largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_downstr_5k_overlap.bed.kinship
3   largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_upstr_5k_overlap.bed.kinship
4     largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_intergenic_overlap.bed.kinship
5             largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_TE_overlap.bed.kinship
6                                            largedata/VCAP/CG_landrace_maize/bedfile/rest_geno



```{r}
cg1 <- read.csv("cache/h2_CG_teosinte_maize.csv")
chg1 <- read.csv("cache/h2_CHG_teosinte_maize.csv")
#chh1 <- read.csv("cache/h2_CHH_teosinte_maize.csv")


cg2 <- read.csv("cache/h2_CG_teosinte_landrace.csv")
chg2 <- read.csv("cache/h2_CHG_teosinte_landrace.csv")
#chh2 <- read.csv("cache/h2_CHH_teosinte_landrace.csv")

cg3 <- read.csv("cache/h2_CG_landrace_maize.csv")
chg3 <- read.csv("cache/h2_CHG_landrace_maize.csv")
#chh3 <- read.csv("cache/h2_CHH_landrace_maize.csv")

```


### Plot:

```{r}
library("beanplot")
library("dplyr")
library("tidyr")
library("ggplot2")


plot_beans <- function(obs, bg, mytrait="asiavg"){
  
  bg1 <- subset(bg, trait %in% mytrait)
  bg1 <- gather(data=bg1, key=k, value="var", 2:6)
  
  #### for trait perse
  bg1$key <- gsub(".*_K", "K", bg1$k)
  #bg1$key <- as.numeric(as.character(bg1$key))
  bg1$var <- as.numeric(as.character(bg1$var))
  
  obs1 <- subset(obs, trait %in% mytrait)
  obs1 <- gather(data=obs1, key=key, value="val", 2:6)
  
  yval <- range(c(obs1$val, bg1$var))
  
  beanplot(var ~ as.factor(key), data = bg1, ll = 0.04, cex=1.5, border = NA,
         what=c(0, 1, 0, 1), col=c(c("antiquewhite3", "black")), cex=1, 
         xlab="", ylab="Variance Explained", main= obs1$pretty_name[1], ylim=c(yval[1], yval[2]+0.02))
  for(i in 1:nrow(obs1)){
    lines(x=c(i-0.3, i+0.3), y=c(obs1$val[i], obs1$val[i]), lwd=2, col="red")
  }
}


```


### sampling results
```{r}
cg1 <- read.csv("cache/h2_CG_teosinte_maize.csv")
s1 <- read.csv("cache/h2_CG_teosinte_maize_sample.csv")


obs <- subset(cg1, h2 > 0.05)


pdf("graphs/var_explained.pdf", width=8, height=8)
for(i in 1:8){
  plot_beans(obs, bg=s1, mytrait=as.character(obs$trait)[i])
}
dev.off()

```
