---
title: "Get GERP score of fixed SNPs in teosinte"
output: html_notebook
author: Gen Xu
---
##Get GERP file
```{r}
library("data.table")
gerp=NULL
for(chri in 1:10)
{
gerpfile=paste("roast.chrom.",chri,".msa.in.rates.full",sep = "")
chr <- fread(gerpfile, header=FALSE, data.table=FALSE)
names(chr) <- c("N", "RS")
chr$chrom <- chri
chr$pos <- 1:nrow(chr)
chr=chr[,c(3,4,1,2)]
gerp=rbind(gerp,chr)
cat("Chromosome length is ",nrow(chr),"\n")
}
write.table(chr, "Maize_GERP_file_AGPv3.txt", sep="\t", row.names=FALSE, quote=FALSE)

```
##Get fixed SNPs in teosinte
```{r}
library("data.table")
freq <- fread("JRIAL2_20samples_All_sep12_2018_AGPv4.maf", header=T, data.table=FALSE)
fix=freq[freq[,4]>=32 & freq[,9]==0,] ###set SNP missing rate <20%, 54,852,914 SNPs were retained
write.table(fix, "20teo_fixed_snp_AGPv4.txt", sep="\t", row.names=FALSE, quote=FALSE)
```

#Get bed file for converting SNPs coordinate from V4 to V3 by Gramme website.Version of SNPs physical position of in GERP file is V3
```{perl}
open(T,"20teo_fixed_snp_AGPv4.txt")||die "Can't open your file!";
open(R,">20teo_fixed_snp_bed");
$l=<T>;
while(<T>)
{
	chomp;
@aa=split;
$start=$aa[1]-1;
$snp="S$aa[0]_$aa[1]";
print R "$aa[0]	$start	$aa[1]	$snp\n";
	
	}
```
##Sample 1M SNPs from fixed SNPs, 8 replications
```{r}
library("data.table")
bed <- fread("20teo_fixed_snp_bed", header=FALSE, data.table=FALSE)
n=nrow(bed)

for(i in 1:8)
{
  id=sort(sample(1:n,1e6))
  bed1=bed[id,]
  out=paste("20teo_fixed_snp_bed",i,sep="")
  write.table(bed1, out, sep="\t", row.names=FALSE, col.na=F,quote=FALSE)
  
}
```

##Get GERP score of each fixed SNP
```{perl}
for($i=1;$i<=10;$i++)
{
%hash=();
$inf="Maize_GERP_file_AGPv3_chr".$i."\.txt";
open(T,$inf)||die "Can't open your file!";
$l=<T>;
while(<T>)
{
	chomp;
@aa=split;
$snp="S$aa[0]_$aa[1]";
$hash{$snp}=$aa[3];
	}
print "$inf\nHash is finshed!";

@bed=glob "*bed";
foreach $f(@bed)
{
	$out="Teo_fix_snp_GERP_".$f."\_chr".$i."\.txt";
open(F,"$f")||die "Can't open your file:$f!";
open(R,">$out");
print R "Chr	Pos	GERP\n";
while(<F>)
{
	chomp;
@bb=split;
$p="S$bb[0]_$bb[2]";
if(exists($hash{$p}))
{print R "$bb[0]	$bb[2]	$hash{$p}\n";}

	}
close(R);
}
}

```
##1 M SNPs were sampled from Whole GERP file
```{r}
library(bigmemory) ##Create, store, access, and manipulate massive matrices 
gerp=read.big.matrix("Maize_GERP_file_AGPv3.txt", type="double", sep="\t", head = TRUE,backingfile = "Maize_GERP_file_AGPv3.back.txt",backingpath = "/lustre/work/jyanglab/gxu6/msfs_teo/Basic_data/GERP", descriptorfile="Maize_GERP_file_AGPv3_des.txt") 

gerp=attach.big.matrix(dget("Maize_GERP_file_AGPv3_des.txt"))
for(i in 1:8)
{
  seed=sort(sample(1:2059403396,1E6))
  d=gerp[seed,]
  out=paste("gerp_random",i,".png",sep="")
  png(out,width=140,height=120,res=600,units="mm")
  par(mar=c(5,4,3,2))
  d=d[,4]
  hist(d,col="gray",las=1,xlab="GERP Score",main="",cex.axis=1.2,cex.lab=1.2,ylab="")
  cat(out,"\n")
  y="Min. 1st Qu.  Median    Mean 3rd Qu.    Max"
  cat(y,"\n")
  x=summary(d)
  cat(x,"\n")
  cat("#############################################\n")
  dev.off()
}

```

#Differences between GERP Score of two groups were significantly (Student’s t-Test)
```{r}
library(data.table)
rf=list.files(path=".",patt="random")
ff=list.files(path=".",patt="fix")
p0=NULL
for(i in rf)
{
  random=fread(i,head=T,data.table=F)
  gerp_r=random[,4]
  for(j in ff)
  {
   fix= fread(j,head=T,data.table=F)
   gerp_f=fix[,3]
   p=t.test(gerp_r,gerp_f)$p.value
   p0=c(p0,p)
  }
}
pp=-log10(p0)

tiff("t_test_p.tiff",width=140,height=130,res=600,units="mm")
par(mar=c(4,3,1,1))
hist(pp,col="gray",xlab="",ylab="",main="",las=1,tck=-0.02,cex.axis=1.5)
dev.off()

```


