---
title: "Get genetic load of each line"
output: html_notebook
author: Gen Xu
---
## Get coordinates of each SNP from VCF file
```{perl}
$in="teo_20samples_sep21_2018_AGPv4_chr$ARGV[0]\.recode.vcf";
open(T,"$in")||die "Can't open your file!";
$out="teo_20samples.chr$ARGV[0]\.pos.txt";
open(R,">$out");
print R "Chr	pos\n";
while(<T>)
{
	chomp;
if(/^#/){next;}
	@aa=split;
	print R "$aa[0]	$aa[1]\n";
	}
close(T,R);

```


## Convert data to AGPv3 coordinates
```{perl}
open(T,"$ARGV[0]")||die "Can't open your file!"; ###$ARGV[0] is file name, eg: teo_20samples.chr1.pos.txt
$ARGV[0]=~s/\.txt//;
$na=$ARGV[0];
open(R,">$na.200bp.bed");
$l=<T>;
while(<T>)
{
	chomp;
	@aa=split;
	$start=$aa[1]-1;
	$end=$aa[1]+198;
print R "$aa[0]	$start	$end\n";
	}
close(T,R);
print "Have got bed file\n";
`seqtk subseq /common/jyanglab/gxu6/B73_v4/maize-genome-V4.fa $na.200bp.bed > $na.200bp.V4.fa`;
print "Have got bed fasta file\n";
`bwa mem -t 10 /common/jyanglab/gxu6/B73_V3/maize-genome-V3 $na.200bp.V4.fa > $na.sam`;
print "Have agalined to B73 of V3\n";
open(T,"$na.sam")||die "Can't open your file!";
open(R,">$na.v3_pos.txt");
print R "Marker	Chr	Pos\n";
while(<T>)
{
	chomp;
if(/^@/ or /^\[M/){next;}
	@aa=split /\t/,$_;
	@bb=split /\-/,$aa[0];
	@cc=split /\:/,$aa[0];
	$bb[0]=~s/\:/\_/;
	$mk="S$bb[0]";
	$nm="NM:i:0";
	if($aa[2]==$cc[0] && $aa[11] eq $nm)
	{print R "$mk	$aa[2]	$aa[3]\n";}
	
	}
close(T,R);
`rm $na.sam $na.200bp.bed $na.200bp.V4.fa`;
print "Tusk has been finsed\n";
```

## get GERP Score of each SNP
```{r}
library(data.table)
library(Ropt)

get_gerp=function(i)
  {fi=qq("teo_20samples.chr{i}.pos.v3_pos.txt")
p=fread(fi, header=T,data.table=F) 
f=qq("/common/jyanglab/gxu6/msfs_teo/Basic_data/GERP/Maize_GERP_file_AGPv3_chr{i}.txt")
d=fread(f, header=T,data.table=F) 
d1=d[p[,3],]
if(nrow(d1)==nrow(p))
{cat("The same row of chr",i,"\n")}
d1=cbind(p,d1[,4])
colnames(d1)[4]="GERP_Score"
d1=d1[order(d1[,2],d1[,3]),]
out=qq("teo_20samples_gerp_chr{i}.txt")
write.table(d1,out,quote = F,col.na=T,row.names = F,sep="\t")
}
arg=getarg()
do.call(get_gerp,arg)
```

# get GERP Score of each SNP in the whole vcf file
```{perl}
open(T,"teo_20samples_gerp_chr$ARGV[0]\.txt")||die "Can't open your file!";
open(R,">teo_20samples_chr$ARGV[0]\__gerp_SNP\.txt");
$l=<T>;print R "$l";
while(<T>)
{
	chomp;
	@aa=split;
if($aa[3]>0){print R "$_\n";}
	}
close(T,R);

$f="teo_20samples_chr$ARGV[0]\__gerp_SNP.txt";
open(T,"$f")||die "Can't open your file!";
while(<T>)
{
	chomp;
@aa=split;
$hash{$aa[0]}=$aa[3];
		}
print "Chr$ARGV[0]\ Hash finished!\n";
$vcf="teo_20samples_sep21_2018_AGPv4_chr$ARGV[0]\.recode.vcf";
open(F,"$vcf")||die "Can't open your file!";
$out="teo_20samples_chr$ARGV[0]\_whole_gerp_SNP.txt";
open(R,">$out");
print R "Chr	Pos	GERP\n";
while(<F>)
{
	chomp;
	if(/^#/){next;}
@bb=split;
$mk="S$bb[0]_$bb[1]";
	if(exists($hash{$mk}))
	{print R "$bb[0]	$bb[1]	$hash{$mk}\n";}
	else{print R "$bb[0]	$bb[1]	NA\n";}
	}

```


## get genetic load 
```{r}
##caculate the genetic load in the region
##method:for example, one region, we have 100 SNPs, 20 SNPs are GERP SNP(gerp>0)
##genetic load=20/100
library(data.table)
library(Ropt)
get_load=function(i,co,win)
  {
  gerp_f=qq("teo_20samples_chr{i}_whole_gerp_SNP.txt")
  g_f=qq("/common/jyanglab/gxu6/msfs_teo/Basic_data/WGS/teo_20samples_sep21_2018_AGPv4_chr{i}.recode.vcf")
gerp=fread(gerp_f, header=T,data.table=F) 
g=fread(g_f,head=T,skip=51,select = c(1,2,co),data.table=F)
na=unlist(strsplit(colnames(g)[3],"_"))[1]
colnames(g)[1:2]=colnames(gerp)[1:2]
g=merge(g,gerp,by=c("Chr","Pos"))
g=g[order(g[,1],g[,2]),] 
 g=g[-grep("\\./\\.",g[,3]),]
 start=1;end=start+win-1
 re=NULL
 while(end<=max(g[,2]))
 {
   d=g[g[,2]>=start & g[,2]<=end,]
   if(nrow(d)==0)
   {res=c(i,start,end,0)}
   else{
     de=length(which(d[,4]>0))
     load=de/nrow(d)
     res=c(i,start,end,load)
   }
   re=rbind(re,res)
   start=start+win;end=start+win-1
   cat(start,"---",end,"\n")
 }
 colnames(re)=c("Chr","Start","End","G_load")
 
 out=qq("{na}.chr{i}.load.txt")
 write.table(re,out,quote = F,col.na=T,row.names = F,sep="\t")
}
arg=getarg()
do.call(get_load,arg)

##Rscript get_load_teo.r i=1 co=10 win=10000 > JRIAL2A_Chr8.log
#windowsize is 10KB

##conbine results according to chromosomes
conb=function(id)
  {re=NULL
for(i in 1:10)
{
  f=qq("{id}.chr{i}.load.txt")
  d=fread(f,head=T,data.table=F) 
  re=rbind(re,d)
}
out=qq("{id}.load.txt")
write.table(re,out,quote = F,col.na=T,row.names = F,sep="\t")
cat(id," has been finshed!","\n")
}

arg=getarg()
do.call(conb,arg)
#Rscript conbine_load.r id=JRIAL2T > JRIAL2T.log

##conbine results according to samples
library(data.table)
library(Ropt)
f=list.files(path=".",patt="load.txt")
d=fread(f[1], header=T,data.table=F)
colnames(d)[4]=gsub(".load.txt","",f[1])
mk=qq("S{d[,1]}_{d[,2]}_{d[,3]}")
d=cbind(mk,d)
for(i in f[-1])
{
 d0= fread(i, header=T,data.table=F) 
 mk=qq("S{d0[,1]}_{d0[,2]}_{d0[,3]}")
 d0=cbind(mk,d0)
 colnames(d0)[5]=gsub(".load.txt","",i)
 
d=merge(d,d0,by=c("mk","Chr","Start","End"))
cat(i," finshed!\n")
}
d=d[order(d[,2],d[,3]),]
d=d[,-1]
out="20teo.genetic_load.txt"
write.table(d,out,quote = F,col.na=T,row.names = F,sep="\t")

```

##To compare the genetic load with landrace and elite maize, we downloaded the hapmap3 unimputed genotype(AGPV3), sanples with read depth more than four were retained. Finally, 95 improved maize inbread lines and 24 landrace lines were keeped.
#Get SNP position of hapmap3
```{perl}
$f="c$ARGV[0]\_hmp321_withGL.vcf.gz";
open(T,"gunzip -c $f|")||die "Can't open your file!";
$out="hmp3_chr$ARGV[0]\.snp.txt";
open(R,">$out");
print R "Chr	Pos\n";
while(<T>)
{
	chomp;
	if(/^#/){next;}
@aa=split;
$lref=length($aa[3]);$lalt=length($aa[4]);
if($lref>1 || $lalt>1){next;} ##keep snps, remove INDEL
print R "$aa[0]	$aa[1]\n";
	
	}
close(T,R);
```

#Get GERP value for each SNP(AGPv3)
```{r}
library(data.table)
library(Ropt)
get_gerp=function(i)
  {fi=qq("hmp3_chr{i}.snp.txt")
p=fread(fi, header=T,data.table=F) 
f=qq("/common/jyanglab/gxu6/msfs_teo/Basic_data/GERP/Maize_GERP_file_AGPv3_chr{i}.txt")
d=fread(f, header=T,data.table=F)
d1=d[p[,2],]
if(nrow(d1)==nrow(p))
{cat("The same row of chr",i,"\n")}
d1=cbind(p,d1[,4])
colnames(d1)[3]="GERP_Score"
out=qq("hmp3_gerp_chr{i}.txt")
write.table(d1,out,quote = F,col.na=T,row.names = F,sep="\t")
}
arg=getarg()
do.call(get_gerp,arg)
```

#Convert physical position from V3 to V4
```{perl}
#####Example file like below:##############
####file name: Chr1.txt ##############
###Chr	Pos##########
###1	555############
###cmd: perl convert_v3_2_v4.pl Chr1.txt##
open(T,"$ARGV[0]")||die "Can't open your file!"; ###$ARGV[0] is file name， suffixis ".txt"", eg: chr1.txt
$ARGV[0]=~s/\.txt//;
$na=$ARGV[0];
open(R,">$na.200bp.bed");
$l=<T>;
while(<T>)
{
	chomp;
	@aa=split;
	$start=$aa[1]-1;
	$end=$aa[1]+198;
print R "$aa[0]	$start	$end\n";
	}
close(T,R);
print "Have got bed file\n";
`seqtk subseq /common/jyanglab/gxu6/B73_V3/maize-genome-V3.fa $na.200bp.bed > $na.200bp.V4.fa`;
print "Have got bed fasta file\n";
`bwa mem -t 10 /common/jyanglab/gxu6/B73_v4/maize-genome-V4.fa $na.200bp.V4.fa > $na.sam`;
print "Have agalined to B73 of V4\n";
open(T,"$na.sam")||die "Can't open your file!";
open(R,">$na.v4_pos.txt");
print R "Marker	Chr	Pos\n";
while(<T>)
{
	chomp;
if(/^@/ or /^\[M/){next;}
	@aa=split /\t/,$_;
	@bb=split /\-/,$aa[0];
	@cc=split /\:/,$aa[0];
	$bb[0]=~s/\:/\_/;
	$mk="S$bb[0]";
	$nm="NM:i:0";
	if($aa[2]==$cc[0] && $aa[11] eq $nm)
	{print R "$mk	$aa[2]	$aa[3]\n";}
	
	}
close(T,R);
#`rm $na.sam $na.200bp.bed $na.200bp.V3.fa`;
print "Tusk has been finsed\n";
```

#Get GERP value for each SNP(AGPv4)
```{perl}
$gf="hmp3_gerp_chr$ARGV[0]\.txt"; #hmp3_gerp_chr1.txt
open(T,"$gf")||die "Can't open your file!";
while(<T>)
{
	chomp;
@aa=split;
$mk="S$aa[0]_$aa[1]";
$hash{$mk}=$aa[2];
}
print "Hash has been finsed!";

$in="hmp3_AGPV3_chr$ARGV[0]\.v4_pos.txt"; ##hmp3_AGPV3_chr4.v4_pos.txt
open(F,"$in")||die "Can't open your file!";
$out="hmp3_AGPV3_chr$ARGV[0]\.v4_pos_GERP.txt";
open(R,">$out");
$l=<F>;print R "Chr	Pos	GERP\n";
while(<F>)
{
	chomp;
@bb=split;
if(exists($hash{$bb[0]}))
	{print R "$bb[1]	$bb[2]	$hash{$bb[0]}\n"}
	}
close(T,R);
```

#Change the VCF from V3 to V4
```{perl}
$pf="hmp3_AGPV3_chr$ARGV[0]\.v4_pos.txt"; #hmp3_AGPV3_chr1.v4_pos.txt
open(T,"$pf")||die "Can't open your file!";
while(<T>)
{
	chomp;
@aa=split;
$hash{$aa[0]}="$aa[1]	$aa[2]";
}
print "Hash has been finsed!";

$in="hmp3_AGPV3_chr$ARGV[0]\_128samples_DP4.vcf";
open(T,"$in")||die "Can't open your file!";
$out="hmp3_AGPV3_chr$ARGV[0]\_128samples_DP4.vcf1";
open(R,">$out");
while(<T>)
{
	chomp;
	if(/^#/){print R "$_\n";next;}
@bb=split /\t/,$_,3;
$mk="S$bb[0]\_$bb[1]";
if(exists($hash{$mk}))
	{print R "$hash{$mk}	$bb[2]\n"}
	}
close(T,R);
`rm $in`;
`mv $out $in`;
```

#Get genetic load in 128 hapmap3 sample
```{r}
library(data.table)
library(Ropt)
get_load=function(i,co,win) ##i is chr, co:10-137, win is windowsize,bp
  {
  gerp_f=qq("hmp3_AGPV3_chr{i}.v4_pos_GERP.txt")
  g_f=qq("hmp3_AGPV4_chr{i}_128samples_DP4.vcf")
gerp=fread(gerp_f, header=T,data.table=F) 
g=fread(g_f,head=T,skip=21,select = c(1,2,co),data.table=F)
na=colnames(g)[3]
colnames(g)[1:2]=colnames(gerp)[1:2]
g=merge(g,gerp,by=c("Chr","Pos"))
g=g[order(g[,1],g[,2]),] 
 g=g[-grep("\\./\\.",g[,3]),]
 start=1;end=start+win-1
 re=NULL
 while(end<=max(g[,2]))
 {
   d=g[g[,2]>=start & g[,2]<=end,]
   if(nrow(d)==0)
   {res=c(i,start,end,0)}else{
     de=length(which(d[,4]>0))
     load=de/nrow(d)
     res=c(i,start,end,load)
   }
   re=rbind(re,res)
   start=start+win;end=start+win-1
   cat(start,"---",end,"\n")
 }
 colnames(re)=c("Chr","Start","End","G_load")
 
 out=qq("{na}.chr{i}.load.txt")
 write.table(re,out,quote = F,col.na=T,row.names = F,sep="\t")
}
arg=getarg()
do.call(get_load,arg)
##Rscript get_load_hmp3.r i=1 co=10 win=10000

##conbine results according to chromosomes
library(data.table)
library(Ropt)
conb=function(id)
  {re=NULL
for(i in 1:10)
{
  f=qq("{id}.chr{i}.load.txt")
  d=fread(f,head=T,data.table=F) 
  re=rbind(re,d)
}
out=qq("{id}.load.txt")
write.table(re,out,quote = F,col.na=T,row.names = F,sep="\t")
cat(id," has been finshed!","\n")
}

arg=getarg()
do.call(conb,arg)
##Rscript conbine_load.r id=A272 > A272.log

##conbine results according to samples
library(data.table)
library(Ropt)
f=list.files(path=".",patt="load.txt")
d=fread(f[1], header=T,data.table=F)
colnames(d)[4]=gsub(".load.txt","",f[1])
mk=qq("S{d[,1]}_{d[,2]}_{d[,3]}")
d=cbind(mk,d)
for(i in f[-1])
{
 d0= fread(i, header=T,data.table=F) 
 mk=qq("S{d0[,1]}_{d0[,2]}_{d0[,3]}")
 d0=cbind(mk,d0)
 colnames(d0)[5]=gsub(".load.txt","",i)
 
d=merge(d,d0,by=c("mk","Chr","Start","End"))
cat(i," finshed!\n")
}
d=d[order(d[,2],d[,3]),]
d=d[,-1]
out="teosinte.genetic_load.txt"
write.table(d,out,quote = F,col.na=T,row.names = F,sep="\t")
```

#Get differentially genetic load region(DGLR)
```{r}
library(data.table)
library(Ropt)
get_dglr=function(input1,input2,out)
{
d1=fread(input1, header=T,data.table=F)
d2=fread(input2, header=T,data.table=F)
mk1=qq("{d1[,1]}_{d1[,2]}_{d1[,3]}")
mk2=qq("{d2[,1]}_{d2[,2]}_{d2[,3]}")
d1=cbind(mk1,d1)
d2=cbind(mk2,d2)
cmk=intersect(d1[,1],d2[,1])
d1=d1[d1[,1]%in%cmk,]
d1=d1[order(d1[,2],d1[,3]),]
d2=d2[d2[,1]%in%cmk,]
d2=d2[order(d2[,2],d2[,3]),]
#if(d1[,1]==d2[,1]){cat("Marker is the same\n")}
nc1=ncol(d1)
nc2=ncol(d2)
#d1=d1[d1[,2]==ch,]
#d2=d2[d2[,2]==ch,]
r=NULL
li=nrow(d2)
cat("Total line is ",li,"\n")
for(i in 1:nrow(d1))
{
  d1a=d1[i,]
  d2a=d2[i,]
  x=as.numeric(d1a[1,5:nc1])
  y=as.numeric(d2a[1,5:nc2])
  m_x=mean(x,na.rm=T)
  m_y=mean(y,na.rm=T)
m_x_y=mean(x,na.rm=T)-mean(y,na.rm=T)
x[1]=x[1]+0.0000000001
p=t.test(x,y)$p.value
d0=unlist(c(d1[i,2:4],m_x,m_y,m_x_y,p)) 
r=rbind(r,d0)
cat("Now is line ",i,"\n")
}
colnames(r)[4:7]=c("m_x","m_y","x-y","P-value")
write.table(r,out,quote = F,col.na=T,row.names = F,sep="\t")
}
arg=getarg()
do.call(get_dglr,arg)
##nohup Rscript get_dglr.r input1="20teo.genetic_load.txt" input2="landrace.genetic_load.txt" ch=1 out="20teo_landrace.dglr.txt" &     

```




