---
title: "VCAP results"
output: NULL
date: 09-28-2019
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('..//')) 
#library(tidyverse)
```


## get Results
                                                                                             V1
1       largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_body_overlap.bed.kinship
2 largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_downstr_5k_overlap.bed.kinship
3   largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_gen_upstr_5k_overlap.bed.kinship
4     largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_intergenic_overlap.bed.kinship
5             largedata/VCAP/CG_landrace_maize/bedfile/CG_landrace_maize_TE_overlap.bed.kinship
6                                            largedata/VCAP/CG_landrace_maize/bedfile/rest_geno


### Bar plot

CG teosinte and maize
```{r}

library("dplyr")
library("tidyr")
library("ggplot2")


mybarplot <- function(df){
  
  #df <- df[order(df$h2, decreasing = TRUE),]
  p <- ggplot(df, aes(x=factor(pretty_name, levels=subset(df, k%in%"DMR")$pretty_name), 
                      y=var, fill=k), position = position_stack(reverse = TRUE)) +
    geom_bar(stat="identity") +
    coord_flip() +
    theme_bw() +
    xlab("") +
    ylab("") +
    geom_hline(yintercept=0.05, linetype="dotted") +
    scale_x_discrete(position = "top") +
    geom_vline(xintercept=0.05, linetype="dotted") +
    # https://www.color-hex.com/color-palette/73961
    
    scale_fill_manual(values=c("#cc4141", "#d3d3d3"),
                      name=c(""),
                      labels=c("DMR", "Genome - DMR")) +
    
    
    theme(legend.position="top", axis.text=element_text(size=12), axis.title=element_text(size=15) )
  #########
  return(p)
}



cg1 <- read.csv("cache/h2_CG_teosinte_maize_cleaned.csv")

pdf("graphs/barplot_CG_teosinte_maize_nofeature.pdf", width = 10, height=6)
mybarplot(df=cg1)
dev.off()  

cg2 <- read.csv("cache/h2_CG_teosinte_landrace_cleaned.csv")
pdf("graphs/barplot_CG_teosinte_landrace_nofeature_cleaned.pdf", width = 10, height=6)
mybarplot(df=cg2)
dev.off()  

cg3 <- read.csv("cache/h2_CG_landrace_maize_cleaned.csv")
pdf("graphs/barplot_CG_landrace_maize_nofeature_cleaned.pdf", width = 10, height=6)
mybarplot(df=cg3)
dev.off()  

```

```{r}
chg1 <- read.csv("cache/h2_CHG_teosinte_maize_cleaned.csv")

pdf("graphs/barplot_CHG_teosinte_maize_cleaned.pdf", width = 8, height=4)
mybarplot(df=chg1)
dev.off()  

chg2 <- read.csv("cache/h2_CHG_teosinte_maize_cleaned.csv")
pdf("graphs/barplot_CHG_teosinte_landrace_cleaned.pdf", width = 8, height=4)
mybarplot(df=chg2)
dev.off()  

chg3 <- read.csv("cache/h2_CHG_teosinte_maize_cleaned.csv")
pdf("graphs/barplot_CHG_landrace_maize_cleaned.pdf", width = 8, height=8)
mybarplot(df=chg3)
dev.off()  
```

