---
title: "Circos plot"
output: html_notebook
author: Jinliang Yang
date: 05-23-2019
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../')) 
#library(tidyverse)
```


### DMR results from Gen

Note some rows are duplicated in the 100-bp `data.table`.


```{r}
library("data.table")
cg <- fread("/common/jyanglab/shared/Gen_Xu/Meth_DMR_MNase_ChIA-PET/CG_pop_meth_DMR_shoot_MNaseHS_Chia_pet2.txt", data.table=FALSE)
#names(cg)[7:9] <- c("DMR", "MNaseHS", "ChIA-PET")
cg$uid <- paste(cg$Chr, cg$Start, cg$End, sep="_")
cg0 <- cg[!duplicated(cg$uid), c(1:6, ncol(cg)) ]




length(unique(cg$uid))

bed <- bed[!duplicated(bed$uid),]

##  find the non-unique ids
tb <- as.data.frame(table(cg$uid))
table(tb$Freq)

#       1        2        3        4        5        6        8       10
# 20153572   884521     3710    19305        7     2141      119        2

tb <- subset(tb, Freq > 1)
sub <- subset(cg, uid %in% tb$Var1)

mnase <- 



cg$DMR1 <- 1
cg$MNase1 <- 1
cg$chia1 <- 1

cg[is.na(cg$DMR),]$DMR1 <- 0
cg[is.na(cg$MNaseHS),]$MNase1 <- 0
cg[is.na(cg$"ChIA-PET"),]$chia1 <- 0


```

## Gen's annotation of V4 genome

24 rows are duplicated, not a problem.
Chr start from 0 (should be 1, all inclusive), but other bps (start and end) are inclusive.

```{r}
bed <- fread("data/07-23-2019genomic_feature.bed", data.table=FALSE)
names(bed) <- c("chr", "start", "end", "feature")
bed$uid <- paste(bed$chr, bed$start, bed$end, sep="_")
length(unique(bed$uid))

##  find the non-unique ids
tb <- as.data.frame(table(bed$uid))
tb <- subset(tb, Freq > 1)
sub <- subset(bed, uid %in% tb$Var1)

bed <- bed[!duplicated(bed$uid),]

bed$bp <- bed$end - bed$start

library("plyr")
f <- ddply(bed, .(feature), summarise,
           tot = sum(bp))
#       feature        tot
#1         Exon   65401079
#2 Gene_down_5k  224979995
#3   Gene_up_5k  224745042
#4   Intergenic  316358525
#5       Intron   89397790
#6           TE 2567864865
```

Not terribly wrong, because there are overlaps.



# Assign features for the 100-bp tiles

```{r}
library("GenomicRanges")

assign_feature <- function(cg, gff, minbp=50L, feas){
  # assign v4 gff genomic features to a table
  # cg: table to be assigned [data.frame, =[,c("Chr", "Start", "End")]]
  # gff: gff file [data.frame, =[,c("chr", "start", "end", "feature")]]
  # minbp: min overalp bp [num, =50L]
  # feas: features to be assigned [chr, NULL]
 
  grc <- with(cg, GRanges(seqnames=Chr, IRanges(start=Start, end=End)))
  #table(gff$feature)
  
  for(i in 1:length(feas)){
    
    ### map features to the 100-bp tiles
    f <- subset(gff, feature %in% feas[i])
    grf <- with(f, GRanges(seqnames=chr, IRanges(start=start, end=end), att=feature))
    message(sprintf("###>>>> Processing feature [%s], query length [%s] and subject length [%s] ...", 
                    feas[i], length(grc), length(grf)))
    
    ####### 
    tb <- findOverlaps(query=grf, subject=grc, minoverlap=minbp)
    tb <- as.matrix(tb)

    cg$newf <- 0
    ## even for overlapped features, they will merge them together
    cg[tb[,2],]$newf<- 1
    names(cg)[ncol(cg)] <- feas[i]
  }
  return(cg)
}
```


## Okay, let's assign genomics features to the 100-bp tiles

```{r}
out <- assign_feature(cg=cg0, gff=bed, minbp=50L, feas=c("Exon", "Gene_down_5k", "Gene_up_5k", "Intergenic", "Intron", "TE"))

sum(out$TE)/nrow(out) #0.7240033
sum(out$Intergenic)/nrow(out) #0.1502257
sum(out$Intron)/nrow(out) #0.04232835
sum(out$Exon)/nrow(out) #0.03078087
sum(out$Gene_up_5k)/nrow(out) #0.09587195
sum(out$Gene_down_5k)/nrow(out) #0.09324796

```

Merge with DMR.

```{r}
dmr <- fread("/common/jyanglab/shared/Gen_Xu/Meth_DMR_MNase_ChIA-PET/Input_file/CG_DMR.bed", data.table=FALSE)
names(dmr) <- c("chr", "start", "end", "pop", "feature")
dmr <- subset(dmr, pop %in% "Teosinte/Maize")
dmr$bp <- dmr$end - dmr$start
sum(dmr$bp) # 633967


out2 <- assign_feature(cg=out, gff=dmr, minbp=50L, feas="CG")
sum(out2$CG) #636300

```


Merge with MNaseHS.

```{r}
hs <- fread("/common/jyanglab/shared/Gen_Xu/Meth_DMR_MNase_ChIA-PET/Input_file/shoot_MNaseHS.Ranges_V4.bed", data.table=FALSE)
names(hs) <- c("chr", "start", "end")

hs$bp <- hs$end - hs$start
sum(hs$bp) # 11050239
mean(hs$bp) #44.7264
range(hs$bp) #1 760

out2 <- assign_feature(cg=out, gff=dmr, minbp=10L, feas="CG")
sum(out2$CG) #636300

```






```{r}
gff <- read.delim("/common/jyanglab/shared/dbcenter/B73_V4_Annotation_file/maize-genome-V4.gff3", comment.char = "#", header=FALSE)
names(gff) <- c("chr", "source", "feature", "start", "end", "score",
                    "strand", "frame", "attribute")





out <- assign_feature(cg, gff, minbp=50L, feas=c("exon", "five_prime_UTR", "three_prime_UTR", 
                                            "lnc_RNA", "miRNA", "pre_miRNA", "ncRNA_gene", "snRNA"))


head(subset(out, snRNA ==1))
head(subset(gff, feature %in% "snRNA"))

cg1 <- out[, 10:20]
cg1$tot <- apply(cg1, 1, sum)
cg2 <- subset(cg1, tot > 0)
fwrite(cg2, "largedata/cg_pop_meth.csv", sep=",", row.names=FALSE, quote=FALSE)

    
```


```{r}
library("UpSetR")
library("ggplot2")

cg1 <- fread("largedata/cg_pop_meth.csv", data.table=FALSE)

upset(cg1, 
      sets = c("DMR1", "MNase1", "chia1"), 
      intersections=list(list("DMR1", "MNase1"), list("DMR1", "chia1")),
      order.by="DMR1", matrix.color="blue", point.size=5,
      sets.bar.color=c("maroon","blue","orange"))


#names(cg1)
upset(cg1, 
      sets = c("DMR1", "MNase1","chia1","exon","five_prime_UTR","three_prime_UTR","lnc_RNA"),
      #intersections=list(list("DMR1", "five_prime_UTR"), list("DMR1", "three_prime_UTR"), list("DMR1", "lnc_RNA")),
      #order.by="DMR1", 
      matrix.color="blue", point.size=5)
      #sets.bar.color=c("maroon","blue","orange"))

upset(cg1, 
      sets = c("DMR1", "MNase1","chia1","exon","five_prime_UTR","three_prime_UTR","lnc_RNA"),
      intersections=list(list("DMR1", "five_prime_UTR"), list("DMR1", "three_prime_UTR"), list("DMR1", "lnc_RNA"),
                         list("DMR1", "MNase1"), list("DMR1", "chia1")),
      #order.by="DMR1", 
      matrix.color="blue", point.size=5)
      #sets.bar.color=c("maroon","blue","orange"))


upset(cg1, 
      sets = c("DMR1", "MNase1","chia1","exon","five_prime_UTR","three_prime_UTR","lnc_RNA"),
      intersections=list(list("DMR1", "five_prime_UTR"), list("DMR1", "three_prime_UTR"), list("DMR1", "lnc_RNA"),
                         list("DMR1", "MNase1"), list("DMR1", "chia1", "five_prime_UTR")),
      #order.by="DMR1", 
      matrix.color="blue", point.size=5)
      #sets.bar.color=c("maroon","blue","orange"))

```



```{r}
#install.packages('UpSetR')
library("UpSetR")
library("ggplot2")

movies <- read.csv( system.file("extdata", "movies.csv", package = "UpSetR"), 
                    header=T, sep=";" )

require(ggplot2); require(plyr); require(gridExtra); require(grid);
## Loading required package: ggplot2
## Loading required package: plyr
## Loading required package: gridExtra
## Loading required package: grid
upset(movies, 
      sets = c("Action", "Comedy", "Drama"), 
      order.by="degree", matrix.color="blue", point.size=5,
      sets.bar.color=c("maroon","blue","orange"))
```






