---
title: "Get fq from CyVerse and Submit to SRA"
author: Jinliang Yang
date: 09-22-2017
output: html_notebook
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```


## Data Plan: CyVerse `/iplant/home/yangjl/BS_teo/`

- /iplant/home/yangjl/BS_teo/WGBS_fastq_lz4
- /iplant/home/yangjl/BS_teo/bam_dedup
- /iplant/home/yangjl/BS_teo/teo20_VCF_AGPv4

## Copy data from CyVerse

```{bash}
# cd largedata/
irsync -rKV i:/iplant/home/yangjl/BS_teo/WGBS_fastq .
```

----------------------------------


## gzip it

```{r, eval=FALSE}
### fastq file
### extract and gz fastq files
# for i in *.lz4; do lz4 -d $i; done
# for i in *.fastq; do gzip --fast $i; done
# for i in *.lz4; do rm $i; done

library("huskeR")
files <- list.files(path="largedata/WGBS_fastq", pattern="lz4")
for(i in 1:length(files)){
    shid <- paste0("slurm-script/run_pigz_", i, ".sh")
    cmd1 <- paste0("cd largedata/WGBS_fastq")
    cmd2 <- paste("lz4 -d --rm", files[i], ">", gsub(".lz4", "", files[i]))
    cmd3 <- paste("pigz -p 20", gsub(".lz4", "", files[i]))
    #cmd4 <- paste("rm", files[i])
    cat(c(cmd1, cmd2, cmd3), file=shid, sep="\n", append=FALSE)
}

set_array_job(shid = "slurm-script/run_lz4_pigz.sh",
       shcode = "sh slurm-script/run_pigz_$SLURM_ARRAY_TASK_ID.sh", arrayjobs = "1-40", wd = NULL,
       jobid = "pigz", email = "yangjl0930@gmail.com", runinfo = c(FALSE, "jclarke", "20", "30","8:00:00"))


```

--------------

## Upload via Aspera COmmand line

You may use the following command to upload files via Aspera Command-Line:
ascp -i <path/to/key_file> -QT -l100m -k1 -d <path/to/folder/containing files> subasp@upload.ncbi.nlm.nih.gov:uploads/yangjlisu@gmail.com_3nAyK7sS

Where:
<path/to/key_file> must be an absolute path, e.g.: /home/keys/aspera.openssh
<path/to/folder/containing files> needs to specify the local folder that contains all of the files to upload.

Get the key file.

If you upload your files in your root directory, you will not be able to see them or to select the folder during the submission.
Make a new subdirectory for each new submission. Your submission subfolder is a temporary holding area and it will be removed once the whole submission is complete.
Do not upload complex directory structures or files that do not contain sequence data.

Return back to this page and select preload folder, then continue submission. 
Please note: it takes at least 10 minutes for uploaded files to become available for selection.

```{r}
library("huskeR")

cmd <- paste0("ascp -i largedata/aspera.openssh -TQ -l100m -k1 ",
              "-d /group/jrigrp4/diallel_fq/fastq ",
              "subasp@upload.ncbi.nlm.nih.gov:uploads/yangjl0930@gmail.com_7MfdNojq/GERP-diallel/")
# ascp -i ~/bin/aspera.openssh -TQ -l100m -k1 -d /group/jrigrp4/diallel_fq/fastq subasp@upload.ncbi.nlm.nih.gov:uploads/yangjl0930@gmail.com_7MfdNojq/GERP-diallel/

# ascp -i ~/bin/aspera.openssh -TQ -l1000m -k1 -d /lustre/work/schnablelab/jyang21/GERP-fq/fastq/* subasp@upload.ncbi.nlm.nih.gov:uploads/yangjl0930@gmail.com_7MfdNojq/GERP-diallel/


set_farm_job(slurmsh = "slurm-script/upload_sra.sh",
             shcode = cmd, wd = NULL, jobid = "upload",
             email = "yangjl0930@gmail.com", runinfo = c(FALSE, "bigmemh", "1", "5G", "80:00:00"))

###>>> In this path: cd /home/jolyang/Documents/Github/GERP-diallel
###>>> RUN: sbatch -p bigmemh --mem 5G --ntasks=1 --time=80:00:00 slurm-script/upload_sra.sh

## ssh farm -p 2022

# rm 2920_3807_2920_Y_RIMMA0806-1_R2.fastq.gz
# rm 2918_3807_2918_N_RIMMA0804.1_R2.fastq.gz

```






