---
title: "Re-analysis Studer 2011 NG fine mapping results"
output: html_notebook
author: Jinliang Yang
date: 11-05-2018
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```

# Modelling

```{r}
## Using R/QTL

#install.packages("qtl")
library(qtl)


d <- read.csv("data/Studer_2011_NatGenet_tb1_data-110706_rqtl.csv")
d <- d[-1:-2, ]

d$Year <- as.factor(d$Year)
d$ID <- as.factor(d$ID)
d$Family <- as.factor(Family)
fit <- lm(TILL ~ Year*ID*Family, data=d)

out <- cbind(d$Year, d$ID)

tb1 <- read.cross("csv", file="data/Studer_2011_NatGenet_tb1_data-110706_rqtl.csv",
                  genotype=c("MM","IM", "II"), alleles=c("I","M"), estimate.map=FALSE, na.strings=".", crosstype = "f2")

x <- as.matrix(d[-1:-2, c("Year", "ID","Family")])
x <- apply(x, 2, as.numeric)
tb1 <- calc.genoprob(tb1, step=0, off.end=0, error.prob=0.01)
out.em <- scanone(tb1, pheno.col="TILL", method="em", addcovar=x)

plot(out.em, ylab="LOD score")

summary(out.em, alpha=0.1)

lodint(out.em, 1, 1.5)

effectplot(tb1, mname1="GS1")
effectplot(tb1, mname1="GS2")
effectplot(tb1, mname1="GS6")
   


out2 <- scantwo(tb1)
plot(out2)
```


```


```{r}
library("lme4")
d$TILL <- as.numeric(as.character(d$TILL))
m1 <- lmer(TILL ~ GS1 + GS8 + GS7 + GS4 + GS6 + GS5 + GS2 + GS3 + (1 | Year), data=d)
anova(m1)

fit <- lmer(TILL ~ Line + (1|Year), data=d)
anova(fit)

fit <- lm(TILL ~ Line + Year, data=d)
anova(fit)

fit1 <- lm(TILL ~ as.factor(Year) + GS1 + GS8 + GS7 + GS4 + GS6 + GS5 + GS2 + GS3 + GS6:GS2 + GS6:GS3 + GS5:GS2 + GS5:GS3, data=d)

summary(fit1)
```

```{r}
d$LBIL <- as.numeric(as.character(d$LBIL))

fit2 <- lm(LBIL ~ as.factor(Year) + GS1 + GS8 + GS7 + GS4 + GS6 + GS5 + GS2 + GS3 + GS6:GS2 + GS6:GS3 + GS5:GS2 + GS5:GS3, data=d)
summary(fit2)
```



