---
title: "Calculate overall SFSs and their distributions"
output: html_notebook
author: Jinliang Yang
date: 12-30-2018
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```

## Data shared by Gen:

### `/common/jyanglab/shared/Gen_Xu/mr_basepair`
- This one contains the methylation ratio at base-pair level

### `/common/jyanglab/shared/Gen_Xu/mr_100bptile`
- This one contains the methylation ratio at 100-bp tile


# purpose: treat methylation level per tile as a genotype using arbitrary cutoff 

and then conduct sensitivity test to show cutoff not very sensitive 


```{r, eval=FALSE}
library("data.table")
## concatenate chr1-10 => chrall
cat_mr <- function(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Teosinte/CG", 
                      outdir="largedata/COMET/CG_COMET/"){
    
    ### checking the status
    files <- list.files(path=path, pattern="txt", full.names=TRUE)
    df <- data.frame(file=files, context=files, genotype=files, chr=1)
    df$fid <- gsub(".*\\/", "", df$file)
    df$context <- gsub("_.*", "", df$fid)
    df$genotype <- gsub("\\..*", "", df$fid)
    df$genotype <- gsub(".*_", "", df$genotype)
    df$chr <- gsub(".*chr|\\.100bp.*", "", df$fid)
    
    geno <- as.character(unique(df$genotype))
    for(gi in 1:length(geno)){
      sub <- subset(df, genotype %in% geno[gi])
      if(nrow(sub) != 10){
          message(sprintf("###>>>> ERROR! [ %s ] doesnot have all 10 chrs!", gi))
      }
      
      
      ### concat ten chrs together
      out <- data.frame()
      for(i in 1:10){
        chr <- fread(as.character(sub$file[i]), header=TRUE, data.table=FALSE)
        out <- rbind(out, chr)
      }
      
      message(sprintf("###>>> writing [ %s ], with [ %s ] rows ...", sub$genotype[1], nrow(out)))
      
      outfile <- paste0(outdir, "/", sub("chr10", "chrall", sub$fid[1]))
      fwrite(out, outfile, sep="\t", row.names=FALSE, quote=FALSE )
    }
}
```


### RUN the above function
```{r, eval=FALSE}
library("data.table")
##########
### Teosinte 
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Teosinte/CG", outdir="largedata/mr_100bp/teosinte/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Teosinte/CHG", outdir="largedata/mr_100bp/teosinte/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Teosinte/CHH", outdir="largedata/mr_100bp/teosinte/")


### Landrace
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Landrace/CG", outdir="largedata/mr_100bp/landrace/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Landrace/CHG", outdir="largedata/mr_100bp/landrace/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Landrace/CHH", outdir="largedata/mr_100bp/landrace/")


### Elite
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Elite_Maize/CG", outdir="largedata/mr_100bp/elite/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Elite_Maize/CHG", outdir="largedata/mr_100bp/elite/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Elite_Maize/CHH", outdir="largedata/mr_100bp/elite/")


```





```{r, eval=FALSE}
out$level <- "med"
      out[out$meth >= 0.66, ]$level <- "high"
      out[out$meth <= 0.33, ]$level <- "low"
        
      
      write.table(out, paste0(outdir, sid, "_COMET.csv"), 
                    sep=",", row.names=FALSE, quote=FALSE)

############################################################################
get_sum <- function(path="largedata/COMET/CG_COMET"){
    files <- list.files(path=path, pattern="csv", full.names=T)
    out <- data.frame()
    for(i in 1:length(files)){
        df <- read.csv(files[i])
        sid <- gsub(".*/|_.*", "", files[i])
        message(sprintf("###>>> Processing sample: [ %s ] ...", sid))
        tem <- data.frame(id=sid, high=sum(subset(df, level %in% "high")$size),
                          med=sum(subset(df, level %in% "med")$size),
                          low=sum(subset(df, level %in% "low")$size) )
        
        out <- rbind(out, tem)
    }
    return(out)
}

##########
## CG
res <- get_sum(path="largedata/COMET/CG_COMET")
write.table(res, "cache/COMET_CG_sum_stat.csv", sep=",", row.names=FALSE, quote=FALSE)

## CHG
res <- get_sum(path="largedata/COMET_CHG/CHG_COMET/")
write.table(res, "cache/COMET_CHG_sum_stat.csv", sep=",", row.names=FALSE, quote=FALSE)


stat <- read.csv("cache/COMET_CG_sum_stat.csv")



```




