---
title: "Calculate overall SFSs and their distributions: step2"
output: html_notebook
author: Jinliang Yang
date: 12-12-2018
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```

## Data shared by Gen:

### `/common/jyanglab/shared/Gen_Xu/mr_basepair`
- This one contains the methylation ratio at base-pair level

### `/common/jyanglab/shared/Gen_Xu/mr_100bptile`
- This one contains the methylation ratio at 100-bp tile


# purpose: treat methylation level per tile as a genotype using arbitrary cutoff 

and then conduct sensitivity test to show cutoff not very sensitive 

### Concatenate data by chrs

### Concatenate by lines
=> to matrix

```{r, eval=FALSE}
library("data.table")

getcat <- function(path="largedata/mr_100bp/teosinte", context="CpG", cols=3:22, BINSIZE=100){
    
    files <- list.files(path=path, pattern=context, full.names = TRUE)  
    message(sprintf("###>>> found [ %s ] files with pattern=[%s]", length(files), context))
    
    
    ### format the first file 
    f1 <- fread(files[1], data.table=FALSE)
    f1$uid <- paste(f1$Chr, f1$Start, f1$End, sep="_")
    fid <- gsub(".*\\/|\\..*", "", files[1])
    names(f1)[4] <- fid
    fout <- f1[, c("uid", fid)]
        
    for(i in 2:length(files)){
        fi <- fread(files[i], data.table=FALSE)
        fi$uid <- paste(fi$Chr, fi$Start, fi$End, sep="_")
        fid <- gsub(".*\\/|\\..*", "", files[i])
        names(fi)[4] <- fid
        fout <- merge(fout, fi[, c("uid", fid)], by="uid", all=TRUE)
    }
 
    outfile <- paste0(path, "_", context, "_matrix.csv")   
    fwrite(fout,  outfile, sep=",", row.names=FALSE, quote=FALSE)   
}


### apply the function:
getcat(path="largedata/mr_100bp/teosinte", context="CpG", cols=3:22, BINSIZE=100)
getcat(path="largedata/mr_100bp/teosinte", context="CHG", cols=3:22, BINSIZE=100)
getcat(path="largedata/mr_100bp/teosinte", context="CHH", cols=3:22, BINSIZE=100)
#

``` 
  
### From matrix to SFS


  
```{r, eval=FALSE}
library("data.table")

test <- fout[1:10, ]
test$cna <- apply(test, 1, function(x) sum(is.na(x)))
    
fout$cna <- apply(fout, 1, function(x) sum(is.na(x)))
    
getsfs <- function(mxfile="largedata/mr_100bp/teosinte_CpG_matrix.csv")    
    #.SD is a data.table and holds all the values of all columns, except the one specified in by.
    #mx <- as.data.table(mx)
    #res <- cg[, lapply(.SD, mymean), by=bin, .SDcols = paste0("V",3:22)]
    mx <- fread(mxfile, data.table=FALSE)
    #mx <- as.data.frame(mx)
    f <- apply(mx[1:10, -1], 1, getcount)
    sfs <- table(f)
}

mymean <- function(x){
    return(mean(x, na.rm=T))
}

getcount <- function(x, mmin=0.3, mmax=0.7){
    x <- x[!is.na(x)]
    n0 <- sum(x < mmin)
    n2 <- sum(x > mmax)
    n1 <- sum(x >= mmin & x <= mmax)
    return(c(n0, n2, n1))
}


sfs <- getsfs(context="CHG", cols=3:22, BINSIZE=100)
write.table(mysfs, "cache/sfs_test.csv", sep=",", row.names=FALSE, quote=FALSE)

```


### RUN the above function
```{r, eval=FALSE}
library("data.table")
##########
### Teosinte 
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Teosinte/CG", outdir="largedata/mr_100bp/teosinte/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Teosinte/CHG", outdir="largedata/mr_100bp/teosinte/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Teosinte/CHH", outdir="largedata/mr_100bp/teosinte/")


### Landrace
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Landrace/CG", outdir="largedata/mr_100bp/landrace/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Landrace/CHG", outdir="largedata/mr_100bp/landrace/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Landrace/CHH", outdir="largedata/mr_100bp/landrace/")


### Elite
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Elite_Maize/CG", outdir="largedata/mr_100bp/elite/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Elite_Maize/CHG", outdir="largedata/mr_100bp/elite/")
cat_mr(path="/common/jyanglab/shared/Gen_Xu/mr_100bptile/Elite_Maize/CHH", outdir="largedata/mr_100bp/elite/")


```





