---
title: "Calculate overall SFSs and their distributions: step2"
output: html_notebook
author: Jinliang Yang
date: 12-12-2018
---


```{r setup, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
knitr::opts_knit$set(root.dir=normalizePath('../../')) 
#library(tidyverse)
```

## Data shared by Gen:

### `/common/jyanglab/shared/Gen_Xu/mr_basepair`
- This one contains the methylation ratio at base-pair level

### `/common/jyanglab/shared/Gen_Xu/mr_100bptile`
- This one contains the methylation ratio at 100-bp tile


# purpose: treat methylation level per tile as a genotype using arbitrary cutoff 

and then conduct sensitivity test to show cutoff not very sensitive 

### Concatenate data by chrs

### Concatenate by lines
=> to matrix

```{r, eval=FALSE}
library("data.table")

getcat <- function(path="largedata/mr_100bp/teosinte", context="CpG", cols=3:22, BINSIZE=100){
    
    files <- list.files(path=path, pattern=context, full.names = TRUE)  
    message(sprintf("###>>> found [ %s ] files with pattern=[%s]", length(files), context))
    
    
    ### format the first file 
    f1 <- fread(files[1], data.table=FALSE)
    f1$uid <- paste(f1$Chr, f1$Start, f1$End, sep="_")
    fid <- gsub(".*\\/|\\..*", "", files[1])
    names(f1)[4] <- fid
    fout <- f1[, c("uid", fid)]
        
    for(i in 2:length(files)){
        fi <- fread(files[i], data.table=FALSE)
        fi$uid <- paste(fi$Chr, fi$Start, fi$End, sep="_")
        fid <- gsub(".*\\/|\\..*", "", files[i])
        names(fi)[4] <- fid
        fout <- merge(fout, fi[, c("uid", fid)], by="uid", all=TRUE)
    }
 
    outfile <- paste0(path, "_", context, "_matrix.csv")   
    fwrite(fout,  outfile, sep=",", row.names=FALSE, quote=FALSE)   
}


### apply the function:
getcat(path="largedata/mr_100bp/teosinte", context="CpG", cols=3:22, BINSIZE=100)
getcat(path="largedata/mr_100bp/teosinte", context="CHG", cols=3:22, BINSIZE=100)
getcat(path="largedata/mr_100bp/teosinte", context="CHH", cols=3:22, BINSIZE=100)
### apply the function to landrace
getcat(path="largedata/mr_100bp/landrace", context="CpG", cols=3:22, BINSIZE=100)
getcat(path="largedata/mr_100bp/landrace", context="CHG", cols=3:22, BINSIZE=100)
getcat(path="largedata/mr_100bp/landrace", context="CHH", cols=3:22, BINSIZE=100)
### apply the function to maize
getcat(path="largedata/mr_100bp/elite", context="CpG", cols=3:22, BINSIZE=100)
getcat(path="largedata/mr_100bp/elite", context="CHG", cols=3:22, BINSIZE=100)
getcat(path="largedata/mr_100bp/elite", context="CHH", cols=3:22, BINSIZE=100)

``` 
  




